\documentclass{article} 
\begin{document}

\newline

Thrust with a thud. Repeat. Thud. Thud. Thud.
\newline
\newline

Sweat. Blood of labour. Juice of Lust.
\newline
\newline

Thud. Thud. Thud. 
\newline
\newline

Pummel. Pierce. Penetrate. Plug. Plug. Plug the hole.
\newline
\newline

Thud. Thud. Thud. Plug. Plug. Plug.
\newline
\newline

Taste tongue. Skin. Labia. Nipple. Thigh. Sack. Pubes. Pits.
\newline
\newline

Cheek. Crack. Toe. And the male cylindrical brain.
\newline
\newline

Hammer. Hammer. Hammer. All creation, pro and re,
\newline
Could use some Hammer. Hammer. Hammer.
\newline

Bathe in your bodies. Twist. Squat. Lean on your tippy
\newline
Toes and Thud. Thud. Thud.
\newline
\newline

Spread flesh. Unroll each other like floor plans.
\newline
\newline

Hammer. Hammer. Hammer. Thud. Thud. Thud.
\newline
\newline

Spot the Beat if you can. Jizz. Jazz. JizzJazz. 
\newline 
\newline

Jets of JizzJazz. Ick. Poick. Sllllllurp. 
\newline 
\newline

White JizzJazzJuice. Crumpled ghosts of destiny's dead children.
\newline 
\newline

On your knees and  pray into the voids \newline Of JizzJazz. \newline
Squish and Slurp and Suck and Spit. \newline Easy Mantra. \newline
\newline


Go Long. Mileage matters. 
\newline 
And be Long. So does size. 
\newline 
Pulpy throbbing \newline Throat sized tree trunks \newline Is what they
all want. \newline To be bored deep. \newline For some hidden oil.
\newline \newline

Close your eyes and sing your dopamine dripping dirge. 
\newline
\newline

From finger-tip to finger to fingers to fist. Tear each other.
\newline
\newline

I know as well as you 
\newline
That hate and love have 
\newline
Their ultimate expressions 
\newline
In Violence and Sex. 
\newline
Respectively.
\newline

I know this difference.
\newline
But I cannot see it. 
\newline
\newline

How, in the narrow corridors of Human Biology, 
\newline 
Am I, this Asexual freak of Nature, to express my Love?

\end{document}
