\documentclass{article} 

\title{Ditch}

\begin{document} \newline

I once tripped and fell in a ditch. The ditch was shaped like me and
would only go as deep as I could. I made the ditch my home and was too
afraid to leave; what if I fell into another ditch that wasn't my size?
\newline
\newline


In this ditch I passed time by wondering how I really knew that the
ditch-sized-me \textit{belonged} in a ditch my size. I called my
inquiries \textit{Philosophy} and assured myself that I was
\textit{transcending} my ditch by questioning its place in \textit{my}
life. I realized that this ditch would never change and by extension
\textit{I} would never change. All I knew was the ditch, and the only
depth this ditch had was what I knew from my fall into it. 
\newline
\newline


I tried digging the ditch for more depth, but the floor was too hard.
When I put more effort into digging, my fingers bled. Sometimes
I wouldn't care and would keep digging, but other times I would stop
because of the fear that I'd dig myself into irreversible darkness.
I was too afraid to climb out and I was too afraid to dig deep. Fear
stabilized me in the ditch. I was proud of my Philosophy. \newline
\newline


As my Life neared its end, I fondly touched the walls of my ditch with
my weak hands. Just as all my Life was spent in this ditch, all my Death
would be spent in it too; I would have conquered eternity itself! I died
with my mouth and eyes open. My elbows were quivering, my knees felt
tingly, my inhales and exhales grew lengthy. I can't remember when my
breathing stopped, but I remember the ditch getting smaller and smaller,
almost like it was still trying to fit me. \newline

\end{document}
