\documentclass{article} 

\title{Santa Monica}

\begin{document} \newline

Summer high-fived the Pacific 

At Santa Monica Beach.

An engineer - just christened 

Part doctor part philosopher - 

Gulped cold beer to mark 

The vulgar journey's end

At Santa Monica Beach, 

Where Summer pulled up her skirt,

And Beers raced the Sun to bold gold.

\newline \newline

The Sun ordained an early defence.

His beard, sacrificed 

To the fires of propriety

His shirt, pressed 

With the weight of his fears

His accent Greek, 

His humanity the World's.

The elders approved in a quiet hurry 

And gave way 

To Santa Monica Beach,

Where Philosophers surfed

And regrets were pissed.

\newline \newline

We spoke of Art and Culture's cancer.

We spoke of Science and Truth's exile.

We spoke of Politics and punished our souls.

We were served cold pale ales,

And Nostalgia's playlist,

And fried potatoes,

And fried onions,

And fried shrimp.

Here at Santa Monica Beach,

Where Hedonism challenged the Pacific,

And Diving didn't mean ``into water''.

\newline \newline

Love's temperature was high.

We rolled our cigarettes catching glimpses 

Of drunk women and their morality.

``There she goes, smiling at my folly'',

``There she goes, Holy Guacamole!''

Here at Santa Monica Beach,

Where guitars translated Nature's babel,

And parents realized they were children all along.

\newline \newline

And Venus came out,

And the sky went from blue to purple,

And the Moon cast dim shadows,

And the Sun reluctantly set.

We rode to Venice

On green bicycles

Hungry for food and youth,

Silly but immortal,

We entered La Cabana, where

The tortilla chips were fine and crisp,

The guacamole plentiful and zingy,

The burritos heavy and sloppy,

The margaritas sweet and quenching,

Here at Venice Beach,

Refugee camp for Artists,

Shining edge of the Free World.

\newline \newline

We were halved in age,

Doubled in spirits.

Sand rippled,

Stars twinkled,

Universe breathed,

We could tell

At Santa Monica Beach,

Where you got a second chance.

Where you got a second chance.


\end{document}
