\documentclass{article} 
\begin{document}

\newline

\textbf{Do not suppose. Propose.}
\newline

I wanted to go outside when it was a suspiciously inappropriate time to
do so. To keep her from suspecting I needed to tell her. Be forthright,
I told myself quietly. She heard me muttering and sat upright. She
said, ``You're mumbling. Speak up.'' I told her I couldn't explain
a certain desire, and that I was desiring to explain it. She rolled her
eyes, leaned back, and said, ``Here. Come closer babe.'' \newline
\newline

\textbf{Do not propose. Impose.}
\newline

He ordered a round of drinks for all of us despite knowing that I am
desperately, though secretly, working on quitting the filthy habit. He
did it because he has grown comfortable with some game theoretic
notions: Having to explain my growing repugnance of ethanol to five
other end-of-a-hard-day's-workers would be a downer. He told me the next
day, after I gathered my pants from his trash-can - not as pasta-sauce
soaked as I'd feared - that he knew he could rely on my moral
imagination to see sense in last night's actions: ``I knew you'd come
through for me. You knew I needed the drinks more than you didn't need
them.'' I wished he had gone on to say,``And I knew the drinks make you
hate yourself so much that you're willing to embrace whatever company
accepts you, and this makes you hate yourself so much more. You are
logarithmically spiralling into the very thing you are running away
from.'' I smiled at him with nothing to say, unsure of whether I was
enjoying life or death. \newline \newline


\textbf{Do not Impose. Pose.}
\newline

Sometimes I feel there is nothing left to say. That everything
worthwhile has already been uttered. I think, and this is sad to admit,
that all communication ought to be hurling books written by others at
each other.\newline \newline


\end{document}
