\documentclass{article} 
\begin{document}

\newline

One day your fear will be realized. When the phone rings, your body
trembles with a cardiac dub-dub as you press green and hear that a loved
one has died, your fear will be realized. You will squeeze the talking
brick, activate needless features like camera, volume control, and God
forbid google-voice wondering if buttons placed on the sides of phones
were precisely intended for times like this, Man juxtaposing Life's
absurdities with technology's. You will, depending on your mood and
maturity, understand that the speaker is as much on the verge of
self-destruction as you are. That speaking of death is as unbearable as
hearing about it. That this is the precise connotation of the word
``Death'' will dawn on you like it never has before. And in this
exchange of electromagnetically ricocheted utterances, these
everything-that-has-to-be-said-has-been-saids, you swell with thoughts
of profundity. Because you are so far away, geographically and thus
emotionally (yes, to you who especially appreciates that one's
surrounding \textit{stirs} one's being (which is why you moved out here
in the first place), you will concede that being absent from your L.O.'s
surrounding doesn't facilitate a whole lot of mutual stirring, and that
this implies emotional distance, and whether you know it or not, the
word ``emotion'' comes from the Latin \textit{motum} which surprise
surprise means \textit{to stir}.), you can't help but assemble
abstraction upon abstraction, like a theorem far from its axioms, about
the meaning of this Death, the Life swerving implications of this Death,
the what-does-it-mean-to-be-alive didactics of this Death. Of course, it
is natural to feel these things, but except that to you these are less
like feelings and more like contemplations, the realization of which
makes you drop your phone. Because you want to feel. Your cravenness for
feeling is much like the madman in the desert whose thirst is itself
a mirage to him. You pick up your phone, hastily apologize into it,
which looks like an apology \textit{to} it because upon saying ``I'm
coming.'', you hurl your phone at the nearest wall, like this country's
best baseball pitcher, and you watch your phone break into glorious
unfeeling fragmentations. You delight in this new entropy. You scroll
through possible plane tickets but only after worrying about how to
inform your stirrers (and stirrees?) in proximity here; how will they
emotionally nurture you when they don't know the circumstances leading
to your sudden departure, let alone know how emotionally starved you
are. And so you pick a flight, for a paycheck burning \$1800 USD because
you are keenly aware that any layover time will all but make you fall
off the cliffs of your sanity. And when you read the words
``Congratulations! Your Credit Card has been approved'', you feel
a resurgence of appetite for entropy. But your laptop is your last
\textit{convenient} means of communication so you bring your knees to
your chest and hug yourself in a pathetic attempt to squeeze shut your
entropic appetite. You stuff a t-shirt and a pair of boxers into
a backpack and are appalled by hygiene's say in anything. Your phone is
in smithereens so calling a cab will have to be done unconventionally
through your laptop, but this time you're better prepared to receive
a Congratulations. Except you aren't because you've just started
worrying about your inability to produce tears at a time like this. And
you're actually not even really worried about this but about how you
know \textit{precisely} how to produce tears not just now but whenever
you feel like. You simply close your eyes, and conjure images of the
L.O. in their most extraordinary plainness. You see them laugh, and
dwell on the innocence of it. You see them look at the world around,
whether in awe at the spectral sunset over hills, or in dread at
gathering of grey clouds, or in indifference at at bug they just
squished. And most tear-triggeringly of all, you see them do whatever it
is they're devoted to, and dwell on how \textit{lost} they are in it.
And this being \textit{lost} to you is the most relatable and moving
thing; here by \textit{lost} you mean ``removed from all else''. You
know that this precisely is what comes closest to making you feel sad,
if you're capable of feeling anything at all. Because your
inaccessibility into the living space, the being space, of an individual
occupied with what clearly appears to you as being their
\textit{raison}, their ritualistic exercise to keep boredom at bay
(which who said ritual means unthinking? It is really the end point of
thinking, it is \textit{revelation}.), equates with your own loneliness.
That if loneliness meant anything, it is this, that everyone feels it in
relation to everybody else. And now your mentation includes the real
un-metaphysical i.e. physical loss of this L.O., this Lonely Other,
making for a doubly dense pang of sadness, which finally induces you
cry. Like an \textit{Eyeagra falls}. And so you're crying and you mouse
over your address on a javascript rendered map, type in the convenient
abbreviation \textit{LAX}, wait for a javascript rendered pinwheel or
hourglass designed to sustain an illusion of continuum to complete its
animation, view a blurry Congratulations because your eyes are just too
damn sad-sogged and the internet is indifferent. You sling your bag on,
tie your shoes, turn all that you can off, regret that you should have
really done the dishes yesterday when you had the time but were instead
binge watching in today's one of many culturally acceptable ways of
pissing away one's life, lock the door, step outside into an unbearably
indifferent surrounding, get into the car, desperately avoid any talk,
even the smallest of small talk if you can and this means holding back
your blubbering and looking out the window and away from the driver to
avoid making red-eye contact with him (slash her, who knows?). You'd
ponder about quantum teleportation if you had the relaxing space and
circumstance which you so totally are not in possession of now. And now
it occurs to you that you will have to sit in two different airplanes,
one for 14 hours and the other for 5 hours, surrounded by other
indifferent raison fulfilling beings with whom any kind of speech act
ought to be avoided on all possible accounts, and if you do being to cry
and are unlucky to not have an aisle seat and so are stuck and this
makes you cry a little more and an air-hostess looks at you and offers
you something to drink as though rehydration is the answer, you accept
the drink for God knows that's the only way the Universe gives a shit if
it gives one at all. One day, all this will happen and your fear will be
realized. Don't say I didn't warn you.


\end{document}
