\documentclass{article} 
\begin{document}

\newline

A:...

B: Social lubricant. Plain and simple.
\newline
\newline

A:...

B: I wouldn't say they so much \textit{slip} out of my mouth as they
\textit{glide} out of it, at least like before the fourth drink. After
that, yeah, I'll admit to some significant slippage. \newline
\newline
\newline

A:...

B: Speaking to the speech-capable is psychically tense for me. Being
a congenital liar myself, I'm unable to tell if I'm ever being taken
seriously. Which is weird because in order to be a good liar, one ought
to like \textit{gauge} the listener, like stay psychically abreast of
his mentation, by paying attention to the rhythm of his deliberate and
default words with the diaghragm of your like psychic receiver, and by
seeking a pattern in the mess of insecurities/principles
revealed in his countenance, like a psychic Fourier Transform you know,
and by mapping his bodily movements and stases to these very pickled
insecurities/principles he preserves in his skull, etc., all of which
I congenitally do, except that it additionally occurs to me that the
listener could be engaged in surveying \textit{my} mentation,
Fourier Transform and all, and that he now, sub-optically of course,
\textit{sees} me seeing him seeing me and so on. Then it is a matter of
psychic tennis you see, one of us has to commit a fault for it to end.
Or if you prefer, one of us has to truncate this like infinite series
expansion. \newline \newline

A:...

B: That's right. The more I drink, the sooner I commit the fault, or the
fewer terms in the series remain if you will. It's a relief really. The
kind you experience when you take an overdue shit. \newline \newline

A:...

B: Call it narcissism or solipsism or even alcoholism. I don't give
a philosophical fuck.
\newline
\newline

A:...

B: Yes. I love you.
\newline
\newline

\end{document}
